---
title: "Yukon Snow Survey \n Bulletin & Water \n Supply Forecast"
#output: html_document
output: 
  word_document:
      reference_docx: style_template2.docx
date: "2023-09-18"
params:
  year: year
  month: month
  basins: basins
---

```{r setup, include=FALSE}
#rmarkdown::render("C:/Users/estewart/Documents/R/Projects/YGwater/inst/rmd/Snow_bulletin.Rmd", params = list(year=2023, month=3, basins=c("Upper Yukon", "Teslin", "Central Yukon", "Pelly", "Stewart", "White", "Lower Yukon", "Porcupine", "Peel", "Liard", "Alsek")))
knitr::opts_chunk$set(echo = TRUE)
con <- YGwater::hydrometConnect()
```


``` {r test, echo=FALSE}
#print(year)
#print(month)
#print(basins)
```


```{r Functions, echo=FALSE}
# Function to create lake level snow bulletin plots
snowbullWater <- function(location, parameter, years, custom_title) {
  flood <- data$flow_level_flood
  tryCatch({
  plot <-
    YGwater::hydrometContinuous(
      location = location,
      parameter = parameter,
      startDay = paste0(years, "-10-01"),
      endDay = paste0(as.character(as.numeric(years) + 1), '-09-30'),
      years = years,
      returns = "none",
      custom_title = custom_title,
      con = con
    )
  
  
  },
  error = function(e) {
    cat("Error")})
  
  if (exists('flood') &
      !is.null(flood) & parameter %in% c("level", "flow")) {
    if (parameter == "level") {
      plot <- plot +
        ggplot2::geom_hline(
          yintercept = dplyr::filter(flood, ID == station_id)$Flood_level_asl,
          linetype = "dashed",
          color = "red",
          size = 1
        ) +
        ggplot2::annotate(
          "text",
          x = as.POSIXct(paste0(year, "-10-25")),
          y = dplyr::filter(flood, ID == station_id)$Flood_level_asl + (max(plot$data$max)-min(plot$data$min))/20,
          label = "Flood level",
          colour = "red"
        )
    } else {
      plot <- plot +
        ggplot2::geom_hline(
          yintercept = dplyr::filter(flood, ID == station_id)$Flood_flow,
          linetype = "dashed",
          color = "red",
          size = 1
        ) +
        ggplot2::annotate(
          "text",
          x = as.POSIXct(paste0(year, "-10-25")),
          y = dplyr::filter(flood, ID == station_id)$Flood_flow + (max(plot$data$max)-min(plot$data$min))/20,
          label = "Flood level",
          colour = "red")
    }
    
  } else {
    plot <- plot
  }
  
  return(plot)
}

# Function to create basin SWE boxplots
snowbullSWE <- function(loc, basin, year, swe_basins, custom_title) {
  # Subset data
  swe_basin <- swe_basins[swe_basins$location==basin,]
  # Plot
  hydrometDiscrete(location = loc, parameter = "SWE", startDay = 1, tzone = "MST", years = c(year), title = TRUE, custom_title = custom_title, plot_type = "linedbox", plot_scale = 1, save_path = NULL, discrete_data = swe_basin, con = con)
}

# Function for calculating CDDF
getCDDF <- function(temps, year) {

  # Function for calculating cddf of dataframe (with all dates of interest)
calcCDDF <- function(temps) {
  cddf <- 0
  temps$cddf <- NA
  for (d in 1:length(temps$value)) {
    t <- temps$value[d]
    # If temperature is NA
    if (is.na(t)) {
      t <- 0
    }
    # If yesterday's cddf is 0 and todays temp is >= 0, keep cddf at 0
    if (cddf==0 & t>=0) {
      cddf <- 0
    } else { 
      cddf <- cddf - t
      if (cddf<0){cddf <- 0}}
    # Set cddf for that day
    temps$cddf[d] <- cddf
  }
return(temps)
} 


# Keep only sept-june data
temps <- temps[format(temps$datetime, "%m") %in% c("09", "10", "11", "12", "01", "02", "03", "04", "05", "06"),]

# Find first and last year 
first_yr <- format(min(temps$datetime), "%Y")
last_yr <- format(max(temps$datetime), "%Y")

# if (last_yr <= year) {
#   last_yr <- year 
# }

cddf <- data.frame()
# Run over every year
for (y in first_yr:last_yr) {
  # Subset data
    tab <- temps[temps$datetime >= paste0(y, '-09-01') 
                 & temps$datetime < paste0(y+1, '-06-14'),]
  # Only calculate if missing less than 10 days, but only for years that are not in the 'years' list
    if (length(tab$datetime) != 0) {
      if (sum(!is.na(tab$value)) >= 276 | format(min(tab$datetime), "%Y") %in% c(year-1)) {
      cddf_y <- calcCDDF(tab)
      cddf <- rbind(cddf, cddf_y)
    }
    }
}

# Rename columns and remove temp
cddf <- cddf[,c("datetime", "cddf")]
colnames(cddf) <- c("datetime", "value")

return(cddf)
}

```

```{r SWEbasins, include=FALSE}
# Get SWE data for basins 
swe_basins <- YGwater::SWE_basin(year = year,
                                   month = c(3, 4, 5), # c(3)
                                   threshold = 6,
                                   csv = FALSE,
                                   summarise = FALSE)
```
\newpage
  
## PREFACE
The Department of Environment’s Water Resources Branch issues the Yukon Snow Survey Bulletin and Water Supply Forecast three times annually – early March, April and May. The bulletin provides a summary of winter meteorological and streamflow conditions for the Yukon, as well as current snow depth and snow water equivalent observations for 57 locations. This information is used to evaluate the potential for spring flooding caused by both breakup ice jams and large spring snowmelt (freshet) flows. It is important to note that other processes such as summer rain and glacier melt can significantly influence maximum annual water levels in specific Yukon basins. March weather conditions for the Yukon are presented in two maps, one showing temperature anomalies (deviation from climate normals), and another showing precipitation anomalies. Territory-wide snowpack data are presented in a third map showing snow water equivalent (SWE) as a percent of historical median for each station, as well as the basinaveraged estimated SWE for 11 watersheds (or river basins). Complementary meteorological and hydrological data are presented for each basin through a series of five graphs, depending on data availability:

* __Figure A:__ Daily Snow Water Equivalent (SWE) data starting in September at one specific location in the watershed, showing an overview of winter snowpack evolution.
* __Figure B:__ Current, basin-averaged, estimated Snow Water Equivalent (SWE) from snow survey data, compared with historical data, serving as an indicator of potential runoff volumes in the spring (acknowledging that snow sublimation, evapotranspiration, rain and glacier melt also significantly affect runoff).
* __Figure C:__ Monthly winter precipitation (rain and/or snow) compared with historical data (1980-2022 period of record), complementing the information presented in Figure B.
* __Figure D:__ Cumulated degree-days of freezing (CDDF, sum of negative daily temperatures) compared with historical data, functioning as an indicator of winter coldness and overall river ice thickness; variables that influence river ice breakup scenarios in the spring.
* __Figure E:__ Current, estimated daily discharge or measured water level, compared with historical data, representing an overview of the watershed hydrological conditions.



## All basins
```{r All_basins, echo=FALSE, fig.width=10}
# Box plot of SWE of all basins
hydrometDiscrete2 <- function(location=NULL,
                             parameter,
                             startDay = 1,
                             endDay = 365,
                             tzone = "MST",
                             years = NULL,
                             title = TRUE,
                             plot_type = "violin",
                             plot_scale = 1,
                             save_path = NULL,
                             dbPath = "default",
                             discrete_data = NULL)
{
  # # Commented code below is for testing...
  # # location = "08AA-SC01"
  # # parameter = "SWE"
  # # startDay = 1
  # # endDay = 365
  # # tzone = "MST"
  # # years = c(2022)
  # # title = TRUE
  # # plot_scale = 1
  # # plot_type = "boxplot"
  # # save_path = NULL
  # # dbPath ="default"
  # # discrete_data = NULL
  # 
  # #TODO Should give a decent error message if the user requests something that doesn't exist. Station not existing, timeseries not existing, years not available (and where they are), etc.
  # 
  # if (startDay != 1){
  #   startDay <- 1
  #   message("Parameter startDay is not currently in use and has been reset to the default of 1.")
  # }
  # if (endDay != 365){
  #   endDay <- 365
  #   message("Parameter endDay is not currently in use and has been reset to the default of 365.")
  # }
  # 
  # # Checks on input parameters  and other start-up bits------------------
  # if (parameter != "SWE"){
  #   parameter <- tolower(parameter)
  # }
  # 
  # plot_type <- tolower(plot_type)
  # if (!(plot_type %in% c("violin", "boxplot"))){
  #   stop("Parameter 'plot_type' must be one of 'violin' or 'boxplot'")
  # }
  # 
  # if (is.null(years)){
  #   years <- as.numeric(substr(Sys.Date(), 1, 4))
  # } else {
  #   years <- as.numeric(years)
  #   years <- sort(years, decreasing = TRUE)
  #   if (length(years) > 10){
  #     years <- years[1:10]
  #     print("The parameter 'years' can only have up to 10 years. It's been truncated to the first 10 years in the vector.")
  #   }
  # }
  # # Select save path
  # if (!is.null(save_path)){
  #   if (save_path %in% c("Choose", "choose")) {
  #     print("Select the folder where you want this graph saved.")
  #     save_path <- as.character(utils::choose.dir(caption="Select Save Folder"))
  #   }
  # }
  # 
  # 
  # if (is.null(discrete_data)) {
  #   #Connect
  #   con <- hydrometConnect(path = dbPath, silent = TRUE)
  #   on.exit(DBI::dbDisconnect(con))
  # 
  #   # Dealing with start/end dates ----------------------
  #   # Sort out startDay and endDay into actual dates if needed
  #   last_year <- max(years)
  #   leap_list <- (seq(1800, 2100, by = 4))  # Create list of all leap years
  #   tryCatch({
  #     startDay <- as.character(startDay)
  #     startDay <- as.POSIXct(startDay, tz = tzone)
  #     lubridate::year(startDay) <- last_year
  #   }, error = function(e) {
  #     if (last_year %in% leap_list){
  #       if (startDay > 59){
  #         startDay <<- startDay + 1
  #       }
  #     }
  #     startDay <<- as.POSIXct(as.numeric(startDay)*60*60*24, origin = paste0(last_year-1, "-12-31"), tz = "UTC")
  #     startDay <<- lubridate::force_tz(startDay, tzone)
  #   })
  #   tryCatch({
  #     endDay <- as.character(endDay)
  #     endDay <- as.POSIXct(endDay, tz = tzone)
  #     lubridate::year(endDay) <- last_year
  #   }, error = function(e) {
  #     tempStartDay <- lubridate::yday(startDay) #using yday because start is now in proper Date format and needs to be back-converted to yday
  #     if (last_year %in% leap_list){
  #       if (endDay > 59){
  #         endDay <<- endDay + 1
  #       }
  #     }
  #     endDay <<- as.POSIXct(as.numeric(endDay)*60*60*24, origin = paste0(last_year-1, "-12-31 23:59:59"), tz = "UTC")
  #     endDay <<- lubridate::force_tz(endDay, tzone)
  #   })
  #   if (startDay > endDay){ #if the user is wanting a range overlapping the new year
  #     lubridate::year(endDay) <- lubridate::year(endDay)+1
  #     overlaps <- TRUE
  #   } else {
  #     overlaps <- FALSE
  #   }
  # 
  #   day_seq <- seq.POSIXt(startDay, endDay, by = "day")
  # 
  #   #Check for existence of timeseries, then for presence of data within the time range requested.
  #   exists <- DBI::dbGetQuery(con, paste0("SELECT * FROM timeseries WHERE location = '", location, "' AND parameter = '", parameter, "' AND type = 'discrete'"))
  #   if (nrow(exists) == 0){
  #     stop("There is no entry for the location and parameter combination that you specified of discrete data type. If you are trying to graph continuous data use hydrometContinuous.")
  #   } else if (nrow(exists) > 1){
  #     stop("There is more than one entry in the database for the location and parameter that you specified! Please alert the database manager ASAP.")
  #   }
  # 
  # 
  # 
  #   #Find the ts units
  #   units <- DBI::dbGetQuery(con, paste0("SELECT units FROM timeseries WHERE parameter = '", parameter, "' AND location = '", location, "'"))
  # 
  #   # Get the data ---------------------
  #   all_discrete <- DBI::dbGetQuery(con, paste0("SELECT * FROM discrete WHERE location = '", location, "' AND parameter = '", parameter, "' AND sample_date < '", paste0(max(years), substr(endDay, 5, 10)), "'"))
  #   if (nrow(all_discrete) == 0){
  #     stop(paste0("There doesn't appear to be any data for the year and days you specified: this timeseries starts ",  exists$start_datetime_UTC))
  #   }
  #   all_discrete$target_date <- as.Date(all_discrete$target_date)
  #   all_discrete$sample_date <- as.Date(all_discrete$sample_date)
  #   all_discrete$year <- lubridate::year(all_discrete$target_date)
  #   all_discrete$month <- lubridate::month(all_discrete$target_date)
  #   all_discrete$day <- lubridate::day(all_discrete$target_date)
  #   #Separate, modify, and re-bind feb29 days, if any
  #   feb29 <- all_discrete[all_discrete$month == 2 & all_discrete$day == 29, ]
  #   if (nrow(feb29) > 0){
  #     all_discrete <- all_discrete[!(all_discrete$month == 2 & all_discrete$day == 29), ]
  #     feb29$target_date <- feb29$target_date + 1
  #     feb29$month <- 3
  #     feb29$day <- 1
  #     all_discrete <- rbind(all_discrete, feb29)
  #   }
  # 
  #   #Make a fake date
  #   all_discrete$fake_date <- as.Date(gsub("[0-9]{4}", last_year, all_discrete$target_date))
  #   discrete <- data.frame()
  #   for (i in years){
  #     start <- as.Date(paste0(i, substr(startDay, 5, 10)))
  #     end <- as.Date(paste0(i, substr(endDay, 5, 10)))
  #     if (overlaps){
  #       lubridate::year(end) <- lubridate::year(end) +1
  #     }
  #     new_discrete <- all_discrete[all_discrete$target_date >= start & all_discrete$target_date <= end , ]
  #     discrete <- rbind(discrete, new_discrete)
  #   }
  #   if (nrow(discrete) == 0){
  #     stop("There is no data to graph after filtering for your specified year(s) and day range. Try again with different days.")
  #   }
  # 
  # }
  # 
  # if (!is.null(discrete_data)) {
  #   ## Create all_discrete
  #   all_discrete <- discrete_data
  #   # add fake_date
  #   all_discrete$fake_date <- as.Date(paste0(max(years), "-0", all_discrete$month, "-01" ))
  #   ## Create discrete
  #   discrete <- all_discrete %>% dplyr::filter(year %in% years)
  #   ## Give units
  #   units <- unique(discrete$units)
  # 
  # }
  # 
  # #Make the plot --------------------
  #  colours = c("blue", "black", "darkorchid3", "cyan2", "firebrick3", "aquamarine4", "gold1", "chartreuse1", "darkorange", "lightsalmon4")
  # legend_length <- length(years)
  # plot <- ggplot2::ggplot(all_discrete, ggplot2::aes(x = location, y = value, group = location)) +
  #   ggplot2::labs(x = "", y = if (parameter == "SWE") paste0("SWE (", units, ")") else paste0(stringr::str_to_title(parameter), " (", units, ")")) +
  #   ggplot2::theme_classic() +
  #   ggplot2::theme(legend.position = "right", legend.justification = c(0, 0.95), legend.text = ggplot2::element_text(size = 8*plot_scale), legend.title = ggplot2::element_text(size = 10*plot_scale), axis.title.y = ggplot2::element_text(size = 12*plot_scale), axis.text.x = ggplot2::element_text(size = 9*plot_scale), axis.text.y = ggplot2::element_text(size = 9*plot_scale))
  # if (plot_type == "violin") {
  #   plot <- plot +
  #     ggplot2::geom_violin(draw_quantiles = c(0.5), adjust = 0.7, width = 12, alpha = 0.8, fill = "aliceblue", scale = "width") #Using a scale other than "width" may result in issues for locations where there are many "0" values.
  # } else if (plot_type == "boxplot"){
  #   plot <- plot +
  #     ggplot2::geom_boxplot(outlier.shape = 8 , outlier.size = 1.7*plot_scale, color = "black", fill = "aliceblue", varwidth = TRUE)
  # }
  # plot <- plot +
  #   ggplot2::geom_point(data = discrete, mapping = ggplot2::aes(x = location, y = value, colour = as.factor(year), fill = as.factor(year)), size = plot_scale*3.5, shape = 21) +
  #   ggplot2::scale_colour_manual(name = "Year", labels = unique(discrete$year), values = colours[1:legend_length], aesthetics = c("colour", "fill"), na.translate = FALSE, breaks=unique(stats::na.omit(discrete$year))[1:legend_length])
  # 
  # # Wrap things up and return() -----------------------
  # if (title == TRUE){
  #   if (is.null(discrete_data)){
  #     stn_name <- DBI::dbGetQuery(con, paste0("SELECT name FROM locations where location = '", location, "'"))
  #     titl <- paste0("Location ", location, ": ", stn_name)
  #   } else {
  #     if (!is.null(location)) {
  #       titl <- paste0("Location: ", location)}
  #     else {
  #       titl <- paste0("Location: ", unique(all_discrete$location))
  #       }
  # 
  #   }
  # 
  #   plot <- plot +
  #     ggplot2::labs(title=titl) +
  #     ggplot2::theme(plot.title=ggplot2::element_text(hjust=0.05, size=14*plot_scale))
  # }
  # 
  # #Save it if requested
  # if (!is.null(save_path)){
  #   ggplot2::ggsave(filename=paste0(save_path,"/", location, "_", parameter, "_", Sys.Date(), "_", lubridate::hour(as.POSIXct(format(Sys.time()), tz=tzone)), lubridate::minute(as.POSIXct(format(Sys.time()), tz=tzone)), ".png"), plot=plot, height=8, width=12, units="in", device="png", dpi=500)
  # }
  # 
  # return(plot)
}
all_basins <- swe_basins[swe_basins$month == 5,]
plot <- hydrometDiscrete2(location = "all basins", parameter = "SWE", startDay = 1, tzone = "MST", years = year, title = FALSE, plot_type = "boxplot", plot_scale = 1, save_path = NULL, discrete_data = all_basins)

``` 

## Upper Yukon river basin (Southern lakes / Whitehorse)
```{r Upper Yukon, echo=FALSE}
# Run or don't run following chunks
if ("Upper Yukon" %in% params$basins) {
  include <- TRUE
} else {
  include <- FALSE
}
``` 

```{r UpperYukonRiver_Snow, echo=FALSE, eval=include, out.width='.49\\linewidth', fig.width=5, fig.height=3,fig.show='hold',fig.align='center'}

## A1 Tagish
# Set station ID
station_id <- "09AA-M1"
# Plot SWE
YGwater::hydrometContinuous(
  location = station_id,
  parameter = "SWE",
  startDay = paste0(year, "-09-01"),
  endDay = paste0(year, '-07-01'),
  years = year-1,
  returns = "none",
  custom_title = "Tagish Snow Water Equivalent",
  con = con
)
## A2 Wolf Creek
# Set station ID
station_id <- "29AB-M3"
# Plot SWE
YGwater::hydrometContinuous(
  location = station_id,
  parameter = "SWE",
  startDay = paste0(year, "-09-01"),
  endDay = paste0(year, '-07-01'),
  years = year-1,
  returns = "none",
  custom_title = "Wolf Creek Subalpine Snow Water Equivalent",
  con = con
)

``` 

```{r UpperYukon_basin, echo=FALSE, eval=include, fig.width=10}
# B
# Plotting 
snowbullSWE(loc= "Upper Yukon", basin = "Upper_Yukon",
            year = year, swe_basins = swe_basins, custom_title = "Upper Yukon Basin Monthly Snow Course Data")
``` 

```{r MonthlyPrecip, echo=FALSE, eval=include}
# C
``` 

```{r Whitehorse_CDDF, echo=FALSE}
# D
whitehorse <- DBI::dbGetQuery(con, "SELECT datetime, value FROM measurements_continuous WHERE timeseries_id = 484")

whitehorse <- getCDDF(whitehorse, year)

YGwater::hydrometContinuous(parameter= "CDDF", startDay = "2023-09-01", endDay = "2024-08-31",  years = c(year-1), title = TRUE, custom_title = "Whitehorse CDDF", returns = "none", allowed_missing = 10, plot_scale = 1, save_path = NULL, con = con, continuous_data = whitehorse)
``` 

```{r MarshLake, echo=FALSE, eval=include, fig.width=10}
# E1
# Set station ID
station_id <- "09AB004"
# Plotting
snowbullWater(location = station_id,
              parameter = "level",
              years = year-1,
              custom_title = "Marsh Lake Water Surface Elevation")
``` 

```{r LakeLaberge, echo=FALSE, eval=include, fig.width=10}
# E2
# Set station ID
station_id <- "09AB010"
# Plotting
snowbullWater(location = station_id,
              parameter = "level",
              years = year-1,
              custom_title = "Lake Laberge Water Surface Elevation")
``` 

## Teslin river basin
```{r Teslin, echo=FALSE}
if ("Teslin" %in% params$basins) {
  include <- TRUE
} else {
  include <- FALSE
}
``` 

```{r TeslinBigSalmon_basin, echo=FALSE, eval=include, fig.width=10}
# B
# Plotting
snowbullSWE(loc= "Teslin - Big Salmon", basin = "Teslin_Big_Salmon",
            year = year, swe_basins = swe_basins, custom_title = "Teslin - Big Salmon Basin Monthly Snow Course Data")
``` 

```{r Teslin_CDDF, echo=FALSE, eval=include}
# D
teslin <- DBI::dbGetQuery(con, "SELECT datetime, value FROM measurements_continuous WHERE timeseries_id = 532")

teslin <- getCDDF(teslin, year)

YGwater::hydrometContinuous(parameter= "CDDF", startDay = "2023-09-01", endDay = "2024-08-31", years = c(year-1), title = TRUE, custom_title = "Teslin CDDF", returns = "none", allowed_missing = 10, plot_scale = 1, save_path = NULL, con = con, continuous_data = teslin)

``` 

```{r TeslinLake, echo=FALSE, eval=include, fig.width=10}
# E
# Set station ID
station_id <- "09AE002"
# Plotting
snowbullWater(location = station_id,
              parameter = "level",
              years = year-1,
              custom_title = "Teslin Lake Water Surface Elevation")
``` 

## Central Yukon river basin (Carmacks area)
```{r Central Yukon, echo=FALSE}
if ("Central Yukon" %in% params$basins) {
  include <- TRUE
} else {
  include <- FALSE
}
``` 

```{r CentralYukon_basin, echo=FALSE, eval=include, fig.width=10}
# B
# Plotting
snowbullSWE(loc= "Central Yukon", basin = "Central_Yukon",
            year = year, swe_basins = swe_basins, custom_title = "Central Yukon Basin Monthly Snow Course Data")
``` 

```{r Carmacks_CDDF, echo=FALSE, eval=include}
# D
carmacks <- DBI::dbGetQuery(con, "SELECT datetime, value FROM measurements_continuous WHERE timeseries_id = 540")

carmacks <- getCDDF(carmacks, year)

YGwater::hydrometContinuous(parameter= "CDDF", startDay = "2023-09-01", endDay = "2024-08-31", years = c(year-1), title = TRUE, custom_title = "Carmacks CDDF", returns = "none", allowed_missing = 10, plot_scale = 1, save_path = NULL, con = con, continuous_data = carmacks)

``` 

```{r Nordenskiold, echo=FALSE, eval=include, fig.width=10}
# E
# Set station ID
station_id <- "09AH004"
# Plotting
snowbullWater(location = station_id,
              parameter = "flow",
              years = year-1,
              custom_title = "Nordenskiold River Discharge below Rowlinson Creek")
``` 

## Pelly river basin
```{r Pelly, echo=FALSE}
if ("Pelly" %in% params$basins) {
  include <- TRUE
} else {
  include <- FALSE
}
``` 

```{r PellyRiver_Snow, echo=FALSE, eval=include, out.width='.49\\linewidth', fig.width=5, fig.height=3,fig.show='hold',fig.align='center'}
## A Twin Creeks
# Set station ID
station_id <- "09BA-M7"
# Plot SWE
YGwater::hydrometContinuous(
  location = station_id,
  parameter = "SWE",
  startDay = paste0(year, "-09-01"),
  endDay = paste0(year + 1, '-07-01'),
  years = year-1,
  returns = "none",
  con = con
)

```

```{r Pelly_basin, echo=FALSE, eval=include, fig.width=10}
# B
# Plotting 
snowbullSWE(loc= "Pelly", basin = "Pelly",
            year = year, swe_basins = swe_basins, custom_title = "Pelly Basin Monthly Snow Course Data")
``` 

```{r Faro_CDDF, echo=FALSE, eval=include}
# D
faro <- DBI::dbGetQuery(con, "SELECT datetime, value FROM measurements_continuous WHERE timeseries_id = 500")

faro <- getCDDF(faro, year)

YGwater::hydrometContinuous(parameter= "CDDF", startDay = "2023-09-01", endDay = "2024-08-31", years = c(year-1), title = TRUE, custom_title = "Faro CDDF", returns = "none", allowed_missing = 10, plot_scale = 1, save_path = NULL, con = con, continuous_data = faro)

``` 

```{r PellyRiver, echo=FALSE, eval=include, fig.width=10}
# E
# Set station ID
station_id <- "09BC001"
# Plotting
snowbullWater(location = station_id,
              parameter = "flow",
              years = year-1,
              custom_title = "Pelly River Discharge at Pelly Crossing")
``` 

## Stewart river basin
```{r Stewart, echo=FALSE}
if ("Stewart" %in% params$basins) {
  include <- TRUE
} else {
  include <- FALSE
}
``` 

```{r StewartRiver_Snow, echo=FALSE, eval=include, out.width='.49\\linewidth', fig.width=5, fig.height=3,fig.show='hold',fig.align='center'}
## A Withers Lake
# Set station ID
station_id <- "09DB-M1"
# Plot SWE
YGwater::hydrometContinuous(
  location = station_id,
  parameter = "SWE",
  startDay = paste0(year, "-09-01"),
  endDay = paste0(year + 1, '-07-01'),
  years = year-1,
  returns = "none",
  con = con
)

``` 

```{r Stewart_basin, echo=FALSE, eval=include, fig.width=10}
# B
# Plotting 
snowbullSWE(loc= "Stewart", basin = "Stewart",
            year = year, swe_basins = swe_basins, custom_title = "Stewart Basin Monthly Snow Course Data")
``` 

```{r Mayo_CDDF, echo=FALSE, eval=include}
# D
mayo <- DBI::dbGetQuery(con, "SELECT datetime, value FROM measurements_continuous WHERE timeseries_id = 548")

mayo <- getCDDF(mayo, year)

YGwater::hydrometContinuous(parameter= "CDDF", startDay = "2023-09-01", endDay = "2024-08-31", years = c(year-1), title = TRUE, custom_title = "Mayo CDDF", returns = "none", allowed_missing = 10, plot_scale = 1, save_path = NULL, con = con, continuous_data = mayo)

``` 

```{r StewartRiver, echo=FALSE, eval=include, fig.width=10}
# E
# Set station ID
station_id <- "09DD003"
# Plotting
snowbullWater(location = station_id,
              parameter = "flow",
              years = year-1,
              custom_title = "Stewart River Discharge at Outlet")
``` 

## White river basin
```{r White, echo=FALSE}
if ("White" %in% params$basins) {
  include <- TRUE
} else {
  include <- FALSE
}
``` 

```{r White_basin, echo=FALSE, eval=include, fig.width=10}
# B
# Plotting 
snowbullSWE(loc= "White", basin = "White",
            year = year, swe_basins = swe_basins, custom_title = "White Basin Monthly Snow Course Data")
``` 

```{r WhiteRiver, echo=FALSE, eval=include, fig.width=10}
# E
# Set station ID
station_id <- "09CB001"
# Plotting
snowbullWater(location = station_id,
              parameter = "flow",
              years = year-1,
              custom_title = "White River Discharge at Alaska Highway")
``` 

## Lower Yukon River basin (Dawson area)
```{r Lower Yukon, echo=FALSE}
if ("Lower Yukon" %in% params$basins) {
  include <- TRUE
} else {
  include <- FALSE
}
``` 

```{r LowerYukonRiver_Snow, echo=FALSE, eval=include, out.width='.49\\linewidth', fig.width=5, fig.height=3,fig.show='hold',fig.align='center'}
## A King Solomon Dome
# Set station ID
station_id <- "09EA-SC01"
# Plot SWE
hydrometDiscrete(
  location = station_id,
  parameter = "SWE",
  years = year-1,
  con = con
)

```

```{r LowerYukon_basin, echo=FALSE, eval=include, fig.width=10}
# B
# Plotting 
snowbullSWE(loc= "Lower Yukon", basin = "Lower_Yukon",
            year = year, swe_basins = swe_basins, custom_title = "Lower Yukon Basin Monthly Snow Course Data")
``` 

```{r Dawson_CDDF, echo=FALSE, eval=include}
# D
dawson <- DBI::dbGetQuery(con, "SELECT datetime, value FROM measurements_continuous WHERE timeseries_id = 492")

dawson <- getCDDF(dawson, year)

YGwater::hydrometContinuous(parameter= "CDDF", startDay = "2023-09-01", endDay = "2024-08-31", years = c(year-1), title = TRUE, custom_title = "Dawson CDDF", returns = "none", allowed_missing = 10, plot_scale = 1, save_path = NULL, con = con, continuous_data = dawson)

``` 

```{r YukonRiver, echo=FALSE, eval=include, fig.width=10}
# E
# Set station ID
station_id <- "09CD001"
# Plotting
snowbullWater(location = station_id,
              parameter = "flow",
              years = year-1,
              custom_title = "Yukon River Discharge at White River")
``` 

## Porcupine River basin
```{r Porcupine, echo=FALSE}
if ("Porcupine" %in% params$basins) {
  include <- TRUE
} else {
  include <- FALSE
}
``` 

```{r Porcupine_basin, echo=FALSE, eval=include, fig.width=10}
# B
# Plotting 
snowbullSWE(loc= "Porcupine", basin = "Porcupine",
            year = year, swe_basins = swe_basins, custom_title = "Porcupine Basin Monthly Snow Course Data")
``` 

```{r OldCrow_CDDF, echo=FALSE, eval=include}
# D
oldcrow <- DBI::dbGetQuery(con, "SELECT datetime, value FROM measurements_continuous WHERE timeseries_id = 556")

oldcrow <- getCDDF(oldcrow, year)

YGwater::hydrometContinuous(parameter= "CDDF", startDay = "2023-09-01", endDay = "2024-08-31", years = c(year-1), title = TRUE, custom_title = "Old Crow CDDF", returns = "none", allowed_missing = 10, plot_scale = 1, save_path = NULL, con = con, continuous_data = oldcrow)

``` 

```{r PorcupineRiver, echo=FALSE, eval=include, fig.width=10}
# E
# Set station ID
station_id <- "09FD002"
# Plotting
snowbullWater(location = station_id,
              parameter = "flow",
              years = year-1,
              custom_title = "Porcupine River Discharge at Border")
``` 

## Peel River basin
```{r Peel, echo=FALSE}
if ("Peel" %in% params$basins) {
  include <- TRUE
} else {
  include <- FALSE
}
``` 

```{r Peel_basin, echo=FALSE, eval=include, fig.width=10}
# B
# Plotting 
snowbullSWE(loc= "Peel", basin = "Peel",
            year = year, swe_basins = swe_basins, custom_title = "Peel Basin Monthly Snow Course Data")
``` 

```{r PeelRiver, echo=FALSE, eval=include, fig.width=10}
# E
# Set station ID
station_id <- "10MA001"
# Plotting
snowbullWater(location = station_id,
              parameter = "flow",
              years = year-1,
              custom_title = "Peel River Discharge")
``` 

## Liard River basin
```{r Liard, echo=FALSE}
if ("Liard" %in% params$basins) {
  include <- TRUE
} else {
  include <- FALSE
}
``` 

```{r LiardRiver_Snow, echo=FALSE, eval=include, out.width='.49\\linewidth', fig.width=5, fig.height=3,fig.show='hold',fig.align='center'}
## A Hyland River
# Set station ID
station_id <- "10AD-M2"
# Plot SWE
YGwater::hydrometContinuous(
  location = station_id,
  parameter = "SWE",
  startDay = paste0(year, "-09-01"),
  endDay = paste0(year + 1, '-07-01'),
  years = year-1,
  returns = "none",
  con = con
)

```

```{r Liard_basin, echo=FALSE, eval=include, fig.width=10}
# B
# Plotting 
snowbullSWE(loc= "Liard", basin = "Liard",
            year = year, swe_basins = swe_basins, custom_title = "Liard Basin Monthly Snow Course Data")
``` 

```{r WatsonLake_CDDF, echo=FALSE, eval=include}
# D
watsonlake <- DBI::dbGetQuery(con, "SELECT datetime, value FROM measurements_continuous WHERE timeseries_id = 508")

watsonlake <- getCDDF(watsonlake, year)

YGwater::hydrometContinuous(parameter= "CDDF", startDay = "2023-09-01", endDay = "2024-08-31", years = c(year-1), title = TRUE, custom_title = "Watson Lake CDDF", returns = "none", allowed_missing = 10, plot_scale = 1, save_path = NULL, con = con, continuous_data = watsonlake)

``` 

```{r LiardRiver, echo=FALSE, eval=include, fig.width=10}
# E
# Set station ID
station_id <- "10AA001"
# Plotting
snowbullWater(location = station_id,
              parameter = "flow",
              years = year-1,
              custom_title = "Liard River Discharge at Upper Liard")
``` 

## Alsek River basin
```{r Alsek, echo=FALSE}
if ("Alsek" %in% params$basins) {
  include <- TRUE
} else {
  include <- FALSE
}
``` 

```{r Alsek_basin, echo=FALSE, eval=include, fig.width=10}
# B
# Plotting 
snowbullSWE(loc= "Alsek", basin = "Alsek",
            year = year, swe_basins = swe_basins, custom_title = "Alsek Basin Monthly Snow Course Data")
``` 

```{r AlsekRiver, echo=FALSE, eval=include, fig.width=10}
# E
# Set station ID
station_id <- "08AB001"
# Plotting
snowbullWater(location = station_id,
              parameter = "flow",
              years = year-1,
              custom_title = "Alsek River Discharge above Bates")
``` 

## Drainage Basin and Snow Course

```{r table, fig.width=10, results='asis', echo=TRUE}
tabl <- SWE_station(year=2023, month=month, return_missing = FALSE, source="hydromet")

tabl <- tabl[, c("location_name", "location_id", "sample_date", "depth", "swe", "swe_prevyear", "swe_med", "years", "sub_basin")]

colnames(tabl) <- c("Name", "Number", "Date of Survey", "Snow depth (cm)", "Water content (SWE) (mm)", "Last year SWE (mm)", "Median historical SWE (mm)", "Years of record", "sub_basin")

# tbl <- knitr::kable(tbl, format="html", caption = "Caption")
# 
# tbl <- kableExtra::kable_styling(tbl, bootstrap_options = "striped", font_size = 12, position = "center")
# 
# print(tbl)

# knitr::kable(tbl, align = "c", caption = "Caption") %>%
#   #kableExtra::kbl(table.attr = "style='width:25%;'", caption = "Caption", align = "c") %>%  
#   kableExtra::kable_styling(bootstrap_options = "striped", font_size = 12, position = "center") %>% 
#   kableExtra::pack_rows(index=rowSums(table(tabl$sub_basin,tabl$location_id)))

# tbl %>%
#   kableExtra::kbl(table.attr = "style='width:25%;'", caption = "Caption",align = "c") %>%
#   kableExtra::kable_styling(bootstrap_options = "striped", font_size = 12, position = "center") %>%
#   kableExtra::pack_rows(index=rowSums(table(tabl$sub_basin,tabl$location_id)))

# tbl <- tabl[, c("location_id", "location_name", "sample_date", "depth", "swe", "swe_prevyear", "swe_med", "swe_rat", "years")] %>% 
#   kbl(table.attr = "style='width:25%;'", caption = "Caption",align = "c") %>%  
#   kable_styling(bootstrap_options = "striped", font_size = 12, position = "center") %>% 
#   pack_rows(index=rowSums(table(tabl$sub_basin,tabl$location_id)))

# tbl
#print(tbl)
#knitr::kable(tbl)

flextable::as_grouped_data(tabl, groups = "sub_basin", hide_grouplabel = TRUE) %>% 
  flextable::as_flextable() %>% 
  #flextable::set_header_labels(what = "") %>% 
  flextable::bold(bold = TRUE, part="header") %>% 
  #flextable::align(i = ~ !is.na(sub_basin), align = "left") %>% 
  flextable::align(part="header", align="center") %>%
  flextable::bold(i = ~ !is.na(sub_basin)) %>%
  flextable::bg(bg="#0097A9", part="header") %>%
  flextable::color(color="white", part="header") %>%
  flextable::hline(part="all") %>%
  flextable::vline()



``` 

