---
title: "Water Temperature Report"
output: html_document
params:
  daily_mean_plot: !r NULL
  daily_max_plot: !r NULL
  seven_day_max_plot: !r NULL
  all_ts: !r NULL
  site_name: !r NULL
  highlight_range: !r NULL
---

```{r, echo=FALSE}

all_ts <- params$all_ts
# Get single row which contains maximum recorded value
max_date <- all_ts |> 
  dplyr::filter(value_corrected == max(all_ts$value_corrected, na.rm = TRUE)) |> 
  dplyr::arrange(desc(datetime)) |> 
  dplyr::distinct(value_corrected, .keep_all = TRUE)

```


Data range from `r min(all_ts$datetime, na.rm = TRUE)` to `r max(all_ts$datetime, na.rm = TRUE)`, highlighted data range from `r params$highlight_range[1]` to `r params$highlight_range[2]`.

For site `r params$site_name`, the maximum temperature recording was `r max_date$value_corrected` and occurred on `r as.Date(max_date$datetime)` at `r format(max_date$datetime, "%H:%M %p")`.

## Daily Mean

```{r, echo=FALSE}
params$daily_mean_plot
```

## Daily Max 

```{r, echo=FALSE}
params$daily_max_plot
```

## Seven Day Rolling Average of Daily Max

```{r, echo=FALSE}
params$seven_day_max_plot
```




